
\chapter{Concluding remarks}

%This chapter should include the following sections,


\section{User instructions}
\subsection{Auto validation}
User should give the Android app all the necessary runtime permissions. The smartphone internet data and BLE should be turned on. The app will automatically detect nearby panic button system and notify user once, the validation procedure completes and the details of vehicle and driver are available. If the validation fails the phone will warn user about the situation.
\subsection{Manual validation}
In case of manual validation, user should go to app on his android smartphone and tap on Validate button. This will start the validation procedure with the nearest gateway device and once the validation completes, the user will be notified with the status of validation and the details of the vehicle and driver.
\subsection{Emergency request}
The user can either press the panic button on the \emph{PanicButton device} or scream. In either case the emergency request will be sent to the nearby PCR.
%The section contains a brief user manual.


%\section{Corrections}

%This section document any last minute corrections that would have
%been undocumented in the engineering and fabrication chapter.


\section{Suggestions for next gen}
In the next gen of this device, following things can be modified-
\begin{itemize}
\item Form factor of the device, it can be made smaller.
\item Performance of the scream detection unit can be improved, through application specific training of the SVMs.
\item Porting the audio detection algorithm to a low-power microcontroller.
\end{itemize}
%This section will give your pointers, tips and recommendations for
%the next generation product and will be of great help to the future
%batch of students working on similar products.


\section{Future scope}
This product has a great potential at reducing the number of crime in public transport vehicle. That being said, the current status of product is incapable of fulfilling this vision due to its large form factor and few field trials. 
%This section will give your view point on the product and its possible
%impact in the market with a discussion on the future scope for this
%product.
